Pool Model

### 2023-12-20 pool_model.tex
include values for the diffusion constants
describe figures better

@@

@@

@@

\cmtb{The ABM additional parameters $D_R$, $D_I$, $q$ (At which level of $R_i$ cell division happens) and more parameters describing bacterial division.}

>>>>

        The background shows the resource concentration $[R]$.
        Darker colours indicate less present nutrients.

@@

        We see that in the highly-diffusive homogenous case of subfigure (a), the pool model is a good fit to the \ac{abm} model.
        Heterogeneity and slower diffusion cause larger differences between the two models as can be seen in subfigures (b) and (c).
        The combination of the two effects shows the largest difference between model predictions.
        In subfigure (d), due to the heterogenous cell distribution (see also~\ref{fig:supplement-spatial-initial-config-cells}) and slow diffusion, overall inhibition of species $B$ does not play as large of a role.
        We furthermore note that the total bacteria volume of the \ac{abm} model is always smaller than the \ac{ode} model.
        This is expected, since processes such as diffusion and cells growing outward introduce another time component which is simply assumed to be instantanous in the \ac{ode} model.
        The chosen diffusion constants $D_I=D_R=30.0$\unit{\micro\metre\squared\per\minute} are in the order of small molecules such as $NaCl$ while the lower values $D_I=D_R=5.0$\unit{\micro\metre\squared\per\minute} are around values of Glucose in water.

@@

        & Diffusion $R$             & $D_R$         & $30.0$\unit{\micro\metre\squared\per\minute}\\
        & Diffusion $I$             & $D_I$         & $30.0$\unit{\micro\metre\squared\per\minute}\\
        % Note: this diffusion roughly corresponds to the one of ethanol in water
        % (see https://de.wikipedia.org/wiki/Diffusionskoeffizient#In_Fl%C3%BCssigkeiten)
        % 15.0 µm^2/min = 0.9 m^2/s
        % Ethanol: 0.84 m^2/s

@@
